---
title: "p8105_hw6_th2723"
author: "Tianhui He"
date: "2019/11/24"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
```

```{r Problem1}
#basic setup
birthweight = read.csv("./data/birthweight.csv")
birthweight = birthweight %>% 
  mutate(babysex = as.factor(babysex),
         frace = as.factor(frace),
         mrace = as.factor(mrace),
         malform = as.factor(malform))
```
According to what I learned from biostatistic method class, "stepwise" modeling could help us to choose a best model automatically.
```{r}
best_model = step(lm(bwt~., data = birthweight), direction = "backward")
```
This stepwise function give us the best model using babysex,bhead,blength, delwt,fincome, gaweeks, mheight, mrace, parity, ppwt and smoken as predictors. A brief glance of the 'best model' chosen by R using regression summary. The global p-value shows that it is significant under 0.05 significance level.
```{r}
best_model %>% summary()
```

```{r}
birthweight %>% 
  modelr::add_predictions(best_model) %>% 
  modelr::add_residuals(best_model) %>% 
  ggplot(aes(x = pred, y = resid)) + geom_point() + geom_smooth(se = F) + theme_bw() + labs(x = "Fitted Value", y = 'Residuals', title = "Residuals vs Fitted value") + theme(plot.title = element_text(hjust = 0.5))
```

